Draft

### 2017-09-04 Thesis/Draft.tex
Edit second chapter

\begin{algorithm}
\SetKwData{Left}{left}\SetKwData{This}{this}\SetKwData{Up}{up}
\SetKwFunction{Union}{Union}\SetKwFunction{FindCompress}{FindCompress}
\SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
\Input{$\tau$, $\epsilon$}
\Output{$\hat{S}_{\tau} = \{k: \hat{\mu}_k(T) \geq \tau\}$}
\BlankLine
\emph{Pull each arm once}\;
\For{$t = K+1$ \KwTo $T$}{
  \emph{Pull arm $I_t = \arg \min_{k\leq K} B_k^{APT}(t) = \sqrt{T_k(t)} (|\hat{\mu}_i(t) - \tau|+\epsilon)$}\;
  \emph{Observe reward $X \sim \nu_{I_t}$}\;
}
\caption{Anytime Parameter-free Thresholding Algorithm (Locatelli et al., 2016)}\label{alg:APT}
\end{algorithm}

@@

As noted in Zhong et al. (2017), a simple requirement to correctly
classify arms at the final round is the following. For every arm
\(i \in \{1, ..., K\}\) after the final round \(T\), require \[
\hat{\mu}_{i,T_i(n)} \geq \mu_i - \frac{\mu_i - \tau + \epsilon}{2} \quad \text{if} \quad \mu_i \geq \tau
\] or \[
\hat{\mu}_{i,T_i(n)} \leq \mu_i + \frac{\tau - \mu_i + \epsilon}{2} \quad \text{if} \quad \mu_i < \tau
\] Or simply in terms of the gap between the arm and the threshold as
used in the index by the APT algorithm: \[
| \hat{\mu}_{i, T_i(n)} - \mu_i | \leq \frac{|\mu_i - \tau| + \epsilon}{2} = \frac{\Delta_i}{2}.
\]

Intuitively, this condition makes sense as it ensures that the current
mean estimate is closer to the true mean than to the threshold.
Consequently, there is no arrangement possible in which the arm is
classified wrong while the separation condition holds. Assuming
\(\mu_i < \tau\) and \(\epsilon = 0\), an incorrect classification would
require \(\mu_i < \tau \leq \hat{\mu_i}\). But then
\(| \hat{\mu}_{i, T_i(n)} - \mu_i | \geq |\mu_i - \tau|\), which
violates the separation condition.

@@

Furthermore, we have assumed \(T>2K\) in the statement of Theorem
\ref{theorem:LocatelliTheorem4}. Plugging this in gives \[
T_k(T) - 1 \geq \frac{(T-K)h_k}{H} \geq \frac{(T-1/2T)h_k}{H} = \frac{Th_i}{2H}
\]

@@

\[
T_k(t) \geq T_k(T) - 1 \geq \frac{Th_i}{2H}.
\]

@@

\[
\mathbb{E}[L] = 1 - \mathbb{P}(\xi) \leq 2(\log(T)+1)K \exp(-\frac{1}{64R^2}\frac{T}{H}).
\]

@@

\section{\texorpdfstring{Information Theoretic Complexity of Pure
Exploration Bandits
\label{chap:KullbackLeiblerPureExploration}}{Information Theoretic Complexity of Pure Exploration Bandits }}\label{information-theoretic-complexity-of-pure-exploration-bandits}

@@

\subsection{\texorpdfstring{Complexity Measures for Best-Arm and
Top-\emph{m} Identification
\label{sec:KaufmannEtAl2016}}{Complexity Measures for Best-Arm and Top-m Identification }}\label{complexity-measures-for-best-arm-and-top-m-identification}

Instead of the thresholding bandit problem, Kaufmann et al. (2016)
consider the problem of identifying the best \(m\) out of \(K\) arms,
that is, the Top-\(m\) problem. They describe their a bandit model
\(\nu\) also by \(K\) arms characterized by probability distributions
\(\nu_a\), \(a \in \{1,...,K\}\) with mean \(\mu_a\). As before, a
learner decides at any time step \(t=1,2,...,\) an arm
\(A_t \in \{1,...,K\}\) for which he observes the independent reward
\(Z_{t} \sim \nu_{A_t}\). The learner aims to find the \(m\) out of
\(K\) arms with the largest expected reward. This set of arm indices is
denoted by \(\mathcal{S}_m^*\). Kaufmann et al. write the in decreasing
order sorted means \((\mu_{1}, ..., \mu_{K})\) as the K-tuple
\((\mu_{[1]}, ..., \mu_{[K]})\). Based on this, they require that
\(\mu_{[m]} > \mu_{[m+1]}\) such that the solution \(\mathcal{S}_m^*\)
is unique. The class of bandit problems \(\nu\) for which the latter
condition holds is called \(\mathcal{M}_m\) by Kaufmann et al. At the
end of the sampling procedure, after \(T\) samples (denoted by \(\tau\)
in Kaufmann et al.) the learner is required to return a classification
\(\hat{\mathcal{S}}_m\). This classification is then evaluated by the
loss function
\(\mathcal{L}(T) = \mathbb{I}(\mathcal{S}^*_m \neq \hat{\mathcal{S}}_m)\).
This binary loss is of course very similar to the loss in the
thresholding bandit problem. We can now define a strategy of the learner
as \(\mathcal{A} = ((A_t), T, \hat{\mathcal{S}}_m)\): The strategy
defines how he chooses an arm, how many samples are observed, and how
the arms are classified in the end.

When introducing the thresholding bandit setting, we did not mention the
fact that the budget \(T\) does not need to be fixed upfront. Indeed,
the setting in which the budget is \emph{not} fixed upfront might be
more popular among the best arm identification and top-\(m\) literature.
This setting is called \emph{fixed confidence}, while the setting we
considered so far is called \emph{fixed budget}. In the fixed budget
setting, we run algorithms for \(T\) samples and then compare them based
on their expected loss,
\(\mathbb{E}[\mathcal{L}(T)] = \mathbb{P}(\mathcal{S}^*_m \neq \hat{\mathcal{S}}_m) =: p_t(\nu)\)
as we have seen in \(\autoref{sec:Setup}\). Alternatively, consider a
\(\delta\)-PAC strategy \(\mathcal{A}(\delta)\)for which holds for every
problem \(\nu \in \mathcal{M}_m\) that the classification holds at least
with confidence level \(1-\delta\), that is,
\(\mathbb{P}(\mathcal{S}^*_m = \hat{\mathcal{S}}_m) \geq 1-\delta\). The
strategy has to achieve this level of confidence in its prediction
before it is allowed to stop sampling. This is the fixed confidence
case, in which the budget \(T\) is no longer fixed upfront, but becomes
a random variable. We compare algorithms by their expected number of
draws \(\mathbb{E}_{\nu}[T_{\delta}]\) and prefer those which arrive at
the confidence level \(1-\delta\) with a smaller expected budget.

Following Kaufmann et al. (2016), in the fixed confidence setting, a
family of strategies \(A = (\mathcal{A}(\delta))_{\delta \in (0,1)}\) is
called PAC if for every \(\delta\), \(\mathcal{A}(\delta)\) is
\(\delta\)-PAC. On the other hand, in the fixed budget setting, a family
of strategies \(A = (\mathcal{A}(t))_{t \in \mathbb{N}}\) is called
consistent if \(p_t(\nu) \rightarrow 0\) as \(t \rightarrow \infty\) for
every problem \(\nu \in \mathcal{M}_m\).

Given this setup, we can now follow the arguments of Kaufmann et al.
(2016) to deduce complexity measures for the top-\(m\) problem. As
alluded to earlier, these complexity measures will rely on the
Kullback-Leibler divergence in contrast to the complexity \(H\) used by
Locatelli et al. (2016). Also, when discussing \(H\), we so far
described it as complexity as it measures the difficulty of the problem
by measuring the distance between arms and the threshold. Kaufmann et
al. approach complexity instead from how many samples (what error
probability) one can expect to need in the fixed confidence (fixed
budget) setting. Thus, in order to arrive at their new measure of
complexity, it makes sense to first follow their arguments to a general
lower bound on the sample complexity \(\mathbb{E}_{\nu}[\tau]\) in the
case of fixed confidence top-\(m\) problems. This bound is given in
their Theorem 4 (for common confidence levels of \(\delta \leq 0.15\)).

@@

\begin{equation*}
\mathbb{E}_{\nu}[\tau] \geq \Big[ \sum_{a \in \mathcal{S}^*_m} \frac{1}{KL(\nu_a, \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}^*_m} \frac{1}{KL(\nu_a, \nu_{[m]})} \Big] \der(1-\delta, \delta),
\end{equation*}

where $\der(x,y) := x \log(x/y) + (1-x) \log((1-x)/(1-y))$ is the binary relative entropy, with the convention that $\der(0,0) = \der(1,1) = 0$.
\end{theorem}

To prove this statement for a given \(\delta\)-PAC algorithm
\(\mathcal{A}\), we assume certain continuity conditions (compare
Kaufmann et al. (2016)), with which there exists for every arm
\(a \in \{1, \dots, K\}\) an alternative model
\(\nu' = (\nu_1, \dots, \nu_{a-1}, \nu_a', \nu_{a+1}, \dots, \nu_K)\).
In this alternative model, in accordance with the continuity conditions,
only arm \(a\) is modified. After the modification, the arm
\(\nu_{m+1}\) is now closer to \(\nu_a\) as measured by the
Kullback-Leibler divergence than \(\nu_a'\) is to \(\nu_a\), if
\(\mu_a > \mu_{m+1}\) (consequently, \(\mu_a' < \mu_{m+1}\)). On the
other hand, if \(\mu_a < \mu_{m}\), then \(\nu_a'\) will be moved away
from \(\nu_a\) just enough so that \(\nu_a\) is closer to \(\nu_m\) than
to \(\nu_a'\) (consequently, \(\mu_a' > \mu_m\)). These changes in
distribution make the original set of optimal arms, \(\{1,\dots,m\}\),
no longer optimal under the alternative model \(\nu'\). To compare this
to the thresholding bandit problem, assume that arms \(\nu_{m}\) and
\(\nu_{m+1}\) indirectly define a threshold
\(\tau \in (\mu_{m+1},\mu_m)\). Then, by creating an alternative problem
as described here, we flip arm \(a\) around the implied threshold
\(\tau\) (compare the lower bound proof in \autoref{sec:AppendixAPTLB}).

Given that the strategy returns \(\hat{S}_m\), we know that for the
event \(\mathcal{E} = (\hat{S}_m = \{1, \dots, m\})\) (which is element
of the \(\sigma\)-Algebra \(\mathcal{F}_{T}\) induced by the stopping
time \(T\)), that \(\mathbb{P}_{\nu}(\mathcal{E}) \geq 1-\delta\) and
\(\mathbb{P}_{\nu'}(\mathcal{E}) \leq \delta\) (because fixed confidence
\(\delta\)!). To now give the lower bound on the expected number of
samples, \(\mathbb{E}_{\nu}[\tau]\), we employ the general Lemma given
by the authors for such changes in distribution in bandit models.

\begin{lemma}[Kaufmann et al., 2016] \label{theorem:KaufmannEtAlLemma1}
Let $\nu$ and $\nu'$ be two bandit models with $K$ arms such that for all $a$, the distributions $\nu_a$ and $\nu_a'$ are mutually absolutely continuous. For any almost-surely finite stopping time $\sigma$ with respect to $(\mathcal{F}_t)$,

\begin{equation*}
\sum_{a=1}^{K} \mathbb{E}_{\nu} [N_a(\sigma)] \KL(\nu_a, \nu_a') \geq \sup_{\mathcal{E} \in \mathcal{F}_{\sigma}} \der (\mathbb{P}_{\nu}(\mathcal{E}), \mathbb{P}_{\nu'}(\mathcal{E})),
\end{equation*}

where $d(x,y)$ is the binary relative entropy as defined above.
\end{lemma}

We can apply this Lemma directly on the expected number of draws for
each arm, \(\mathbb{E}_{\nu}[N_a]\). For each arm \(a\), we thus have
\(\KL(\nu_a, \nu_a') \mathbb{E}_{\nu}[N_a] \geq d(1-\delta, \delta)\).
Using the definition of the alternative model above, we get for every
small but fixed \(\alpha > 0\), for every arm \(a \in \{1, \dots, K\}\)
and each arm \(b \in \{m+1, \dots, K\}\):

\begin{equation*}
\mathbb{E}_{\nu}[N_a] \geq \frac{\der(1-\delta, \delta)}{\KL (\nu_a, \nu_{m+1}) + \alpha}
\end{equation*}

and

\begin{equation*}
\mathbb{E}_{\nu}[N_b] \geq \frac{\der(1-\delta, \delta)}{\KL (\nu_b, \nu_{m}) + \alpha}.
\end{equation*}

We can then let \(\alpha \to 0\), sum the bounds on the individual arms
to get the bound on the overall number of draws:

\begin{equation*}
\mathbb{E}_{\nu}[T] = \sum_{a=1}^K \mathbb{E}_{\nu}[N_a] \geq \Big( \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m]})} \Big) \der(1-\delta, \delta)
\end{equation*}

@@

\begin{equation*}
\mathbb{E}_{\nu}[T] \geq \Big( \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m]})} \Big) \log \big(\frac{1}{2.4\delta} \big).
\end{equation*}

Given this lower bound, it becomes clear that the complexity of the
top-\(m\) problem can be lower bounded by the Kullback-Leibler
divergence between arms and the implied threshold between the \(m\)-th
best arm and the \((m+1)\)-th best arm. After all, the latter gives a
lower bound on the effort (in terms of expected number of samples)
required to achieve a certain confidence level. And a problem that
requires a larger effort can be described as more complex. Indeed, in
the case of fixed confidence problems, Kaufmann et al. (2016) describe
problems as having a larger \emph{sampling complexity}.

Following Kaufmann et al. (2016), we can now define the complexity
\(\kappa_C(\nu)\) for the fixed confidence setting as

\begin{equation}
\kappa_C(\nu) = \inf_{A \, \text{PAC}} \lim_{\delta \to 0} \sup \frac{\mathbb{E}_{\nu}[T{\delta}]}{\log \frac{1}{\delta}}. \label{eq:KappaC}
\end{equation}

@@

\begin{equation*}
\kappa_C(\nu) \geq \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m]})}
\end{equation*}

Given this description, we would expect that a complexity measure in a
fixed confidence thresholding bandit probem might involve replacing
\(\mu_{[m]}\) and \(\mu_{[m+1]}\) by the actual threshold \(\tau\) that
divides the group above the threshold from the group below the
threshold.

However, given the problem formulation in Locatelli et al. (2016), we
are mainly interested in complexity measures and algorithms for the
fixed budget setting. As we will see now, the results of Kaufmann et al.
(2016) are more limited for this case. While the authors are able to
provide a bound on their complexity measure in the fixed budget case, it
only applies to the case of \emph{two-armed} bandit models. Consider a
consistent fixed budget strategy \(\mathcal{A}\) (\(p_t(\nu)\) tends to
zero as \(t \rightarrow \infty\)), and define the complexity in the
fixed budget setting as follows:

\begin{equation}
\kappa_B(\nu) = \inf_{A \, \text{consistent}} \big(\lim_{t \to \infty} \sup - \frac{1}{t} \log p_t(\nu)\big)^{-1}.
\end{equation}

While we included the experimenter-fixed \(\delta\) in the definition of
\(\kappa_C\), we now include the experimenter-fixed \(T\) in the
definition of \(\kappa_B\) to disregard it in the complexity measure
after plugging in the lower bound on \(p_t(\nu)\). The resulting lower
bound given in Theorem 12 of Kaufmann et al. (2016):

@@

\begin{equation*}
\lim_{t \to \infty} \sup - \frac{1}{t} \log p_t(\nu) \leq \inf_{(\nu_1', \nu_2') \in \mathcal{M}: \mu_1' < \mu_2'} \frac{\KL(\nu_1', \nu_1) + \KL(\nu_2', \nu_2)}{2}
\end{equation*}
\end{theorem}

For a proof, consider first the two different bandit models, \(\nu\) and
\(\nu'\), where we fix w.l.o.g. \(a^* = 1\) as the best arm in \(\nu\),
while \(a^* = 2\) in \(\nu'\). Note that in this case we don't
necessarily try to fool the algorithm by a change of distribution.
Indeed, we want the algorithm \(\mathcal{A}\) to be consistent for both
problems. Since we are in the fixed budget setting, the stopping time is
fixed at \(T = t\). Even though the correct decision differs between the
two problems, we focus on the event \(A = (\hat{S}_1 = 1)\). Now, we can
apply Lemma 1 as before, as it in essence gives a measure of how
different two bandit models are. Here, we want to know how different
\(\nu\) is from \(\nu'\), and so, given we have only two arms,

\begin{equation*}
\mathbb{E}_{\nu'}[N_1(t)]\KL(\nu_1', \nu_1) + \mathbb{E}_{\nu'}[N_2(t)]\KL(\nu_2', \nu_2) \geq \der(\mathbb{P}_{\nu'}(A),\mathbb{P}_{\nu}(A)))
\end{equation*}

@@

Before we discuss the strategies of Kaufmann et al. (2016) matching the
lower bounds, we now show how lower bounds can be derived very similarly
for the fixed budget thresholding problem.

\subsubsection{Lower Bound for Fixed Budget Thresholding
Problem}\label{lower-bound-for-fixed-budget-thresholding-problem}

In order to derive a bound for the fixed budget problem, Kaufmann et al.
(2016) have focused on the case of the two-armed bandit which is the
most simple version of the top-\(m\) problem. Less than two arms do not
make sense, since then this single arm will always be the best arm. In
the case of the thresholding bandit, however, a single-armed problem
makes still some sense in that we still have to classify this arm
correctly with respect to the threshold. Thus, we can show the following
corollary which gives the a bound on the complexity of the single-armed
thresholding bandit.

>>>>

\begin{algorithm}
\SetKwData{Left}{left}\SetKwData{This}{this}\SetKwData{Up}{up}
\SetKwFunction{Union}{Union}\SetKwFunction{FindCompress}{FindCompress}
\SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
\Input{$\tau$, $\epsilon$}
\Output{$\hat{S}_{\tau} = \{i \in \{1,...,K\}, \hat{\mu}_i(T) \geq \tau\}$}
\BlankLine
\emph{Pull each arm once}\;
\For{$t = K+1$ \KwTo $T$}{
  \emph{Pull arm $I_t = \arg \min_{i \in A} B_i^{APT}(t) = \arg \min_{i \in A} \sqrt{T_i(t)} (|\hat{\mu}_i(t) - \tau|+\epsilon)$}\;
  \emph{Observe reward $X_t \sim \nu_{I_t}$}\;
}
\caption{Anytime Parameter-free Thresholding Algorithm (Locatelli et al., 2016)}\label{alg:APT}
\end{algorithm}

@@

As noted in Zhong et al. (2017), a simple requirement to correctly
classify arms at the final round is the following. For every arm
\(i \in \{1, ..., K\}\) after the final round \(T\), require \[
\hat{\mu}_{i}(T) \geq \mu_i - \frac{\mu_i - \tau + \epsilon}{2} \quad \text{if} \quad \mu_i \geq \tau
\] or \[
\hat{\mu}_{i}(T) \leq \mu_i + \frac{\tau - \mu_i + \epsilon}{2} \quad \text{if} \quad \mu_i < \tau
\] Or simply in terms of the gap between the arm and the threshold as
used in the index by the APT algorithm: \[
| \hat{\mu}_{i}(T) - \mu_i | \leq \frac{|\mu_i - \tau| + \epsilon}{2} = \frac{\Delta_i}{2}.
\]

Intuitively, this condition makes sense as it ensures that the current
mean estimate is closer to the true mean than to the threshold.
Consequently, there is no arrangement possible in which the arm is
classified wrong while the separation condition holds. Assuming
\(\mu_i < \tau\) and \(\epsilon = 0\), an incorrect classification would
require \(\mu_i < \tau \leq \hat{\mu_i}\). But then
\(| \hat{\mu}_{i}(T) - \mu_i | \geq |\mu_i - \tau|\), which violates the
separation condition.

@@

Furthermore, we have assumed \(T>2K\) in the statement of Theorem
\ref{theorem:LocatelliTheorem4}. Plugging this in gives \[
T_k(T) - 1 \geq \frac{(T-K)h_k}{H} \geq \frac{(T-1/2T)h_k}{H} = \frac{Th_k}{2H}
\]

@@

\[
T_k(t) \geq T_k(T) - 1 \geq \frac{Th_k}{2H}.
\]

@@

\[
\mathbb{E}[\mathcal{L}(T)] = 1 - \mathbb{P}(\xi) \leq 2(\log(T)+1)K \exp(-\frac{1}{64R^2}\frac{T}{H}).
\]

@@

\section{\texorpdfstring{Information Theoretic Approaches to Pure
Exploration Bandits
\label{chap:KullbackLeiblerPureExploration}}{Information Theoretic Approaches to Pure Exploration Bandits }}\label{information-theoretic-approaches-to-pure-exploration-bandits}

@@

\subsection{\texorpdfstring{Information Theoretic Complexity Measures in
Top-\(m\) Problems
\label{sec:KaufmannEtAl2016}}{Information Theoretic Complexity Measures in Top-m Problems }}\label{information-theoretic-complexity-measures-in-top-m-problems}

Instead of the thresholding bandit problem, Kaufmann et al. (2016)
consider the problem of identifying the best \(m\) out of \(K\) arms,
that is, the top-\(m\) problem. They describe their bandit model \(\nu\)
by \(K\) arms characterized by probability distributions \(\nu_a\),
\(a \in \{1,...,K\}\), with mean \(\mu_a\). A learner picks at any time
step \(t=1,2,...,\) an arm \(A_t \in \{1,...,K\}\) for which he observes
the independent reward \(Z_{t} \sim \nu_{A_t}\). The learner aims to
find the \(m\) out of \(K\) arms with the largest expected reward. This
set of arm indices is denoted by \(\mathcal{S}_m^*\). Kaufmann et al.
write the means \((\mu_{1}, ..., \mu_{K})\) sorted in decreasing order
as the K-tuple \((\mu_{[1]}, ..., \mu_{[K]})\). Based on this, they
require that \(\mu_{[m]} > \mu_{[m+1]}\) such that the solution
\(\mathcal{S}_m^*\) is unique. The class of bandit problems \(\nu\) for
which the latter condition holds is called \(\mathcal{M}_m\) by Kaufmann
et al. At the end of the sampling procedure, after \(T\) samples
(denoted by \(\tau\) in Kaufmann et al.) the learner is required to
return a classification \(\hat{\mathcal{S}}_m\). This classification is
then evaluated by the loss function
\(\mathcal{L}(T) = \mathbb{I}(\mathcal{S}^*_m \neq \hat{\mathcal{S}}_m)\).
This binary loss is similar to the loss in the thresholding bandit. We
can now define a strategy of the learner as
\(\mathcal{A} = ((A_t), T, \hat{\mathcal{S}}_m)\): The strategy defines
how an arm is chosen, how many samples are observed, and how the arms
are eventually classified.

When introducing the thresholding bandit setting, we did not mention the
fact that the budget \(T\) does not need to be fixed upfront. Indeed,
the setting in which the budget is \emph{not} fixed upfront might be
more popular among the best arm identification and top-\(m\) literature.
This setting is called \emph{fixed confidence}, while the setting we
considered so far is called \emph{fixed budget}. In the fixed budget
setting, we run algorithms for \(T\) samples and then compare them based
on their expected loss,
\(\mathbb{E}[\mathcal{L}(T)] = \mathbb{P}(\mathcal{S}^*_m \neq \hat{\mathcal{S}}_m) =: p_t(\nu)\)
as we have seen in \(\autoref{sec:Setup}\). Alternatively, consider a
\(\delta\)-PAC strategy \(\mathcal{A}(\delta)\)for which it holds for
every problem \(\nu \in \mathcal{M}_m\) that the classification holds at
least with confidence level \(1-\delta\), that is,
\(\mathbb{P}(\mathcal{S}^*_m = \hat{\mathcal{S}}_m) \geq 1-\delta\). The
strategy has to achieve this level of confidence in its prediction
before it is allowed to stop sampling. This is the fixed confidence
case, in which the budget \(T\) is no longer fixed upfront, but turns
into a random variable. Algorithms are then compared by their expected
number of draws \(\mathbb{E}_{\nu}[T_{\delta}]\) and we prefer those
which achieve the confidence level \(1-\delta\) with a smaller expected
budget.

In the fixed confidence setting, a family of strategies
\(A = (\mathcal{A}(\delta))_{\delta \in (0,1)}\) is called PAC if for
every \(\delta\), \(\mathcal{A}(\delta)\) is \(\delta\)-PAC. On the
other hand, in the fixed budget setting, a family of strategies
\(A = (\mathcal{A}(t))_{t \in \mathbb{N}}\) is called consistent if
\(p_t(\nu) \rightarrow 0\) as \(t \rightarrow \infty\) for every problem
\(\nu \in \mathcal{M}_m\).

Given this setup, we can now follow the arguments of Kaufmann et al.
(2016) to derive complexity measures for the top-\(m\) problem. As
alluded to earlier, these complexity measures will rely on the
KL-divergence in contrast to the complexity \(H\) used by Locatelli et
al. (2016). When discussing \(H\), its motivation is that it represents
the difficulty of the problem by measuring the distance between arms and
the threshold. Instead, Kaufmann et al. approach complexity by how many
samples (what error probability) one will need in the fixed confidence
(fixed budget) setting. In order to arrive at their new measure of
complexity, it makes sense to first follow their arguments to a general
lower bound on the sample complexity \(\mathbb{E}_{\nu}[\tau]\) which is
given in their Theorem 4:

@@

\begin{equation*}
\mathbb{E}_{\nu}[\tau] \geq \Big[ \sum_{a \in \mathcal{S}^*_m} \frac{1}{\KL(\nu_a || \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}^*_m} \frac{1}{\KL(\nu_a || \nu_{[m]})} \Big] \der(1-\delta, \delta),
\end{equation*}
\end{theorem}

To prove this statement for a given \(\delta\)-PAC algorithm
\(\mathcal{A}\), we assume certain continuity conditions (compare
Kaufmann et al. (2016)) under which there exists for every arm
\(a \in \{1, \dots, K\}\) an alternative model
\(\nu' = (\nu_1, \dots, \nu_{a-1}, \nu_a', \nu_{a+1}, \dots, \nu_K)\).
In this alternative model, in accordance with the continuity conditions,
only arm \(a\) is modified. After the modification, the arm
\(\nu_{m+1}\) is now closer to \(\nu_a\) as measured by the
Kullback-Leibler divergence than \(\nu_a'\) is to \(\nu_a\), if
\(\mu_a > \mu_{m+1}\) (consequently, \(\mu_a' < \mu_{m+1}\)). On the
other hand, if \(\mu_a < \mu_{m}\), then \(\nu_a'\) will be moved away
from \(\nu_a\) just enough so that \(\nu_a\) is closer to \(\nu_m\) than
to \(\nu_a'\) (consequently, \(\mu_a' > \mu_m\)). These changes in
distribution make the original set of optimal arms, \(\{1,\dots,m\}\),
no longer optimal under the alternative model \(\nu'\). To compare this
to the thresholding bandit problem, assume that arms \(\nu_{m}\) and
\(\nu_{m+1}\) indirectly define a threshold
\(\tau \in (\mu_{m+1},\mu_m)\). Then, by creating an alternative problem
as described here, we flip arm \(a\) around the implied threshold
\(\tau\) (compare the lower bound proof in \autoref{sec:AppendixAPTLB}).

Given the strategy returns \(\hat{S}_m\), we know that for the event
\(\mathcal{E} = (\hat{S}_m = \{1, \dots, m\})\) (which is element of the
\(\sigma\)-Algebra \(\mathcal{F}_{T}\) induced by the stopping time
\(T\)), that \(\mathbb{P}_{\nu}(\mathcal{E}) \geq 1-\delta\) and
\(\mathbb{P}_{\nu'}(\mathcal{E}) \leq \delta\) (because fixed confidence
\(\delta\)!). To give the lower bound on the expected number of samples,
\(\mathbb{E}_{\nu}[\tau]\), we employ the general Lemma given by the
authors for such changes in distribution in bandit models.

\begin{lemma}[Lemma 1, Kaufmann et al., 2016] \label{theorem:KaufmannEtAlLemma1}
Let $\nu$ and $\nu'$ be two bandit models with $K$ arms such that for all $a$, the distributions $\nu_a$ and $\nu_a'$ are mutually absolutely continuous. For any almost-surely finite stopping time $\sigma$ with respect to $(\mathcal{F}_t)$,

\begin{equation*}
\sum_{a=1}^{K} \mathbb{E}_{\nu} [N_a(\sigma)] \KL(\nu_a|| \nu_a') \geq \sup_{\mathcal{E} \in \mathcal{F}_{\sigma}} \der (\mathbb{P}_{\nu}(\mathcal{E}), \mathbb{P}_{\nu'}(\mathcal{E})).
\end{equation*}
\end{lemma}

We apply this Lemma directly on the expected number of draws for each
arm, \(\mathbb{E}_{\nu}[N_a]\). For each arm \(a\), we thus have
\(\KL(\nu_a, \nu_a') \mathbb{E}_{\nu}[N_a] \geq d(1-\delta, \delta)\).
Using the definition of the alternative model above, we get for every
small but fixed \(\alpha > 0\), every arm \(a \in \{1, \dots, K\}\) and
\(b \in \{m+1, \dots, K\}\):

\begin{equation*}
\mathbb{E}_{\nu}[N_a] \geq \frac{\der(1-\delta, \delta)}{\KL (\nu_a || \nu_{m+1}) + \alpha} \quad \text{and} \quad \mathbb{E}_{\nu}[N_b] \geq \frac{\der(1-\delta, \delta)}{\KL (\nu_b || \nu_{m}) + \alpha}.
\end{equation*}

Let \(\alpha \to 0\), sum the individual arms' bounds to get the bound
on the overall number of draws:

\begin{equation*}
\mathbb{E}_{\nu}[T] = \sum_{a=1}^K \mathbb{E}_{\nu}[N_a] \geq \Big( \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a|| \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a|| \nu_{[m]})} \Big) \der(1-\delta, \delta)
\end{equation*}

@@

\begin{equation*}
\mathbb{E}_{\nu}[T] \geq \Big( \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a|| \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a|| \nu_{[m]})} \Big) \log \big(\frac{1}{2.4\delta} \big).
\end{equation*}

Given this lower bound, it is clear that the complexity of the top-\(m\)
problem can be lower bounded by the KL-divergence between arms and the
implied threshold between the \(m\)-th best arm and the \((m+1)\)-th
best arm. The latter gives a lower bound on the effort (in terms of
expected number of samples) required to achieve a certain confidence
level, where a problem that requires a larger effort is described as
more complex. Indeed, in the case of fixed confidence problems, Kaufmann
et al. (2016) describe problems as having a larger \emph{sampling
complexity}.

Following Kaufmann et al. (2016), we define the complexity
\(\kappa_C(\nu)\) in the fixed confidence setting as

\begin{equation}
\kappa_C(\nu) = \inf_{A \, \text{PAC}} \limsup_{\delta \to 0} \frac{\mathbb{E}_{\nu}[T{\delta}]}{\log \frac{1}{\delta}}. \label{eq:KappaC}
\end{equation}

@@

\begin{equation*}
\kappa_C(\nu) \geq \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a || \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a || \nu_{[m]})}
\end{equation*}

Given this description, we would expect that a complexity measure in a
fixed confidence thresholding bandit probem might involve replacing
\(\mu_{[m]}\) and \(\mu_{[m+1]}\) by the actual threshold \(\tau\) that
divides the group above the threshold from the group below the
threshold. But given the setting in Locatelli et al. (2016), we are
mainly interested in complexity measures and algorithms for the fixed
budget problem. The results of Kaufmann et al. (2016) are more limited
for this case. While the authors are able to provide a bound on their
complexity measure in the fixed budget case, it only applies to the case
of \emph{two-armed} bandit models.

Consider a consistent fixed budget strategy \(\mathcal{A}\)
(\(p_t(\nu)\) tends to zero as \(t \rightarrow \infty\)), and define the
complexity in the fixed budget setting as follows:

\begin{equation}
\kappa_B(\nu) = \inf_{A \, \text{consistent}} \big(\limsup_{t \to \infty} - \frac{1}{t} \log p_t(\nu)\big)^{-1}.
\end{equation}

While we included the experimenter-fixed \(\delta\) in the definition of
\(\kappa_C\), we now include the fixed \(T\) in the definition of
\(\kappa_B\) to disregard it in the complexity measure after plugging in
the lower bound on \(p_t(\nu)\). The resulting lower bound given in
Theorem 12 of Kaufmann et al. (2016):

@@

\begin{equation*}
\limsup_{t \to \infty} - \frac{1}{t} \log p_t(\nu) \leq \inf_{(\nu_1', \nu_2') \in \mathcal{M}: \mu_1' < \mu_2'} \max \big\{\KL(\nu_1' || \nu_1), \KL(\nu_2' || \nu_2)\big\}
\end{equation*}
\end{theorem}

For a proof, consider first the two different bandit models, \(\nu\) and
\(\nu'\), where we fix w.l.o.g. \(a^* = 1\) as the best arm in \(\nu\),
while \(a^* = 2\) in \(\nu'\). We require the algorithm \(\mathcal{A}\)
to be consistent for both problems. Since we are in the fixed budget
setting, the stopping time is fixed at \(T = t\). The correct decision
differs between the two problems, and we focus on the event
\(A = (\hat{S}_1 = 1)\). Now, we can apply Lemma 1 from Kaufmann et al.
(2016) as before, as it gives a measure of how different two bandit
models are (it bounds the change in distribution). Here, we want to know
how different \(\nu\) is from \(\nu'\), and, given we have only two
arms,

\begin{equation*}
\mathbb{E}_{\nu'}[N_1(t)]\KL(\nu_1'|| \nu_1) + \mathbb{E}_{\nu'}[N_2(t)]\KL(\nu_2'|| \nu_2) \geq \der(\mathbb{P}_{\nu'}(A),\mathbb{P}_{\nu}(A)))
\end{equation*}

@@

Before we discuss algorithms given in Kaufmann et al. (2016) that match
the lower bounds, we show how lower bounds can be derived very similarly
for the fixed budget thresholding problem.

\subsubsection{\texorpdfstring{Lower Bound for Fixed Budget Thresholding
Problem
\label{sec:LBTBP}}{Lower Bound for Fixed Budget Thresholding Problem }}\label{lower-bound-for-fixed-budget-thresholding-problem}

In order to derive a bound for the fixed budget problem, Kaufmann et al.
(2016) have focused on the setting with two arms which is the most
simple version of the top-\(m\) problem. Less than two arms do not make
sense, since the single arm is by definition the best arm. In the case
of the thresholding bandit, however, a single-armed problem makes still
at least limited sense in that we still have to classify this arm
correctly with respect to the threshold. Thus, we can show the following
corollary which gives a bound on the complexity of the single-armed
thresholding bandit.
